On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-02-07 v-research_experiment-alpha.tex
minor changes
minor changes (weakness definition)

\documentclass{article}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[toc,page]{appendix}
\usepackage[gen]{eurosym}
\usepackage{tabularx}
\usepackage{epigraph}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{csquotes}% Recommended
\usepackage{rotating}
\usepackage[style=numeric]{biblatex}
% \bibliography{<mybibfile>}% ONLY selects .bib file; syntax for version <= 1.1b
\addbibresource{../../97-literature/literature.bib}% Syntax for version >= 1.2

\usepackage{graphicx}
\graphicspath{{./00-images/}}

@@

\begin{definition}{\bf Region: Weakness and Vulnerability --}\label{def:weakness}
	When a Region $\region\subseteq\agent$ of an agent
	$\agent\in\agentuniverse$ is identified as Weakness $\Weakness$ (i.e.
	representing a weakness introduced by the agent into any phase of
	production, e.g.  of the secure process development life-cycle, of any
	system or subsystem) iff there exists $\world\in\possibleworlds$ such
	that $\World,\Weakness\models\Diamond\exists\Weakness',\Vulnerability'.~
	\po{\Weakness'}{\Vulnerability'}$, where $\Weakness'\subseteq\Weakness$, and
	$\Vulnerability'\subseteq\Vulnerability$ is a Region of an agent $\agent'\in\agentuniverse$.
\end{definition}

>>>>

\documentclass{article}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[toc,page]{appendix}
\usepackage[gen]{eurosym}
\usepackage{tabularx}
\usepackage{epigraph}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{csquotes}% Recommended
\usepackage{rotating}
\usepackage[style=numeric]{biblatex}
% \bibliography{<mybibfile>}% ONLY selects .bib file; syntax for version <= 1.1b
\addbibresource{literature.bib}% Syntax for version >= 1.2

\usepackage{graphicx}
\graphicspath{{./images/}}

@@

\begin{definition}{\bf Region: Weakness and Vulnerability --}\label{def:weakness}
	A Region $\region\subseteq\agent$ of an agent
	$\agent\in\agentuniverse$ is defined as Weakness $\Weakness$ (i.e.
	representing a weakness introduced by the agent into any phase of
	production, e.g.  of the secure process development life-cycle, of any
	system or subsystem) iff there exists $\world\in\possibleworlds$ such
	that $\World,\Weakness\models\Diamond\exists\Weakness',\Vulnerability'.~
	\po{\Weakness'}{\Vulnerability'}$, where $\Weakness'\subseteq\Weakness$, and
	$\Vulnerability'\subseteq\Vulnerability$ is a Region of an agent $\agent'\in\agentuniverse$.
\end{definition}
